---
title: "PredictAssignmentRCode"
output: html_document
---


```{r}
options(warn=-1)
library(caret)
library(randomForest)
library(Hmisc)

library(foreach)
library(doParallel)
set.seed(4356)
```

###Getting the data
Read the data with read.csv from local drive
The raw training data will be in a data-frame variable called training and raw testing data in  testing. 
```{r}
setwd("D:/Coursera Assignment")
data <- read.csv("pml-training.csv")
```

First we need to reimport data ignoring "#DIV/0!" values
```{r}
data <- read.csv("pml-training.csv",na.strings=c("#DIV/0!") )
```

Cast to numeric values for the specified columns
```{r}
cData <- data
for(i in c(8:ncol(cData)-1)) {cData[,i] = as.numeric(as.character(cData[,i]))}
```

We will select as feature only the column with a 100% completion rate, as seen in analysis phase, the completion rate in this dataset is very binary
```{r}
featuresnames <- colnames(cData[colSums(is.na(cData)) == 0])[-(1:7)]
features <- cData[featuresnames]

xdata <- createDataPartition(y=features$classe, p=3/4, list=FALSE )
training <- features[xdata,]
testing <- features[-xdata,]
```

We will use parallel concept for processing with the foreach and doParallel package
```{r}
registerDoParallel()
model <- foreach(ntree=rep(150, 4), .combine=randomForest::combine) %do% randomForest(training[-ncol(training)],training$classe, ntree=ntree)
```

To evaluate the model now, we will use the confusionmatrix method
```{r}
predictionsTr <- predict(model, newdata=training)
confusionMatrix(predictionsTr,training$classe)


predictionsTe <- predict(model, newdata=testing)
confusionMatrix(predictionsTe,testing$classe)
```

###Conclusion
As seen by the result of the confusionmatrix, the model is good and efficient because it has an accuracy of 0.997 
Lowest value is 0.992 for the sensitivity of the class C
So its also a good sensitivity & specificity values on the testing dataset.
